### 2020-06-18 v0.1.5/assets/FlowChart/flowchart.tex
build based on b33f934

\def\lw{2mm}        % Arrow line width
\def\mw{2cm}        % Minimum width of component
\def\mh{1.75cm}     % Minimum height of component
\def\trianglecoordinate{2mm}    % Starting coordinate clock input triangle of components

@@

\tikzset{
    border/.style = { 
        draw, circle, minimum width=1cm, thick
    },
    pics/Task/.style={
        code = {
            \node [border, align=center](-edge){#1};
    }}
    }

\begin{document}
    \begin{tikzpicture}
        \draw pic (t1) {Task={Writer\\Task}};
        \draw (3,0) pic (t2) {Task={Reader\\Task}};
        \draw[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->] (t1-edge.east) -- (t2-edge.west);
    \end{tikzpicture}
\end{document}

>>>>

\def\lw{1mm}        % Arrow line width
\def\mw{2cm}        % Minimum width of component
\def\mh{1cm}     % Minimum height of component
\def\trianglecoordinate{2mm}    % Starting coordinate clock input triangle of components

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=0.75\mw, minimum height=\mh, very thick
    },
    pics/Component/.style ={
        code = {
            \node [border, align=center](-edge){#1};
    }}
    }

\tikzset{
    decisionborder/.style = { 
        draw, diamond,, minimum width=1*\mw, minimum height=\mh, very thick
    },
    pics/Decision/.style ={
        code = {
            \node [decisionborder, align=center](-decisionedge){#1};
    }}
    }

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 0.75cm, row sep = 1cm, 
            nodes={anchor=center}]{
        \draw pic (b1) {Component={Start}}; \&
        \draw pic (b2) {Decision={Inspect}}; \&
        \draw pic (b3) {Component={Initialize}}; \&
        \draw pic (b4) {Component={Run}}; \&
        \draw pic (b5) {Component={Terminate}}; \\
        };
        \begin{scope}[very thick, >={Triangle[width=2mm,length=2mm]}]
            \draw[->] (b1-edge.east) -- (b2-decisionedge.west);
            \draw[->] (b2-decisionedge.east) -- node[midway, anchor=west, align=center, rotate=90]{Suitable\\For Simulation} (b3-edge.west);
            \draw[->] (b3-edge.east) -- (b4-edge.west);
            \draw[->] (b4-edge.east) -- (b5-edge.west);
            \draw[-] (b2-decisionedge.south) -- node[midway, anchor=east, align=center]{Unsuitable\\For Simulation} ++(0cm, -1cm) coordinate(a);
            \draw[->] (a) -| (b5-edge.south);
        \end{scope}
    \end{tikzpicture}
\end{document}
